Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2024-03-01 writing/paper_mcd19a2.qmd
Made the annual AQS comparison more sophisticated.

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ on `r scales::comma(l$n.cell.times)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values. In a year-level comparison, against `r l = tar_read(satellite.vs.aqs.yearly); scales::comma(l$n.cell.times)` cell-years of AQS annual means, we found a correlation with the original satellite values of `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.

>>>>

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ on `r scales::comma(l$n.cell.times)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.

`r l = tar_read(satellite.vs.aqs.yearly); ""` In a year-level comparison, we took cell-years with at least `r min.days.for.annual.aqs` days of AQS observations and `r l$min.days.in.month` days per month of satellite observations for at least `r l$min.months` months. Obtaining `r scales::comma(l$n.cell.times)` cell-years, we compared official AQS annual means to the yearly means of satellite observations, computed with daily means weighted according to how many days of the year to which each day was closest. The result was a correlation with the original satellite values of `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.
